Network analysis of code to code comparison

### 2015-09-24 014-network-analysis-code-to-code.Rmd
Don't like package loading messages

```{r warning=FALSE}
library("textreuse")
library("stringr")
library("dplyr")
library("igraph")
source("R/extract-date.R")
source("R/plot_network.R")
```

>>>>

```{r message=FALSE}
library("textreuse")
library("stringr")
library("dplyr")
library("igraph")
source("R/extract-date.R")
source("R/plot_network.R")
```
